---
title: "Mapping prevalence of respiratory illness in Zimbabwe"
output: html_document
---


```{r, include=FALSE, echo=FALSE, eval=FALSE}
library(sf)
library(mgcv)
library(raster)
library(lubridate)
library(sf)
library(disarmr)
library(gratia)
library(leaflet)
library(wesanderson)
library(knitr)

#opts_chunk$set(fig.width=12, fig.height=8)

setwd("~/Documents/Work/Lnl/GitRepos/fn-covid19-prev-pred")
source('R/prevalence_predictor_mgcv_st_grid.R')

# Testing prevalence_predictor_mgcv_st_grid
resp_ill <- read.csv("~/Documents/Work/Lnl/covid_modeling_ZWE/data/dhs_cluster_illness_rate_gps_041620.csv")

# Organize data
df_trim <- data.frame(lng = resp_ill$LONGNUM,
                                 lat = resp_ill$LATNUM,
                                 n_positive = resp_ill$count_any, 
                                 n_trials = resp_ill$total_children_asked)

# Prepare covariates
pred_raster_hw <- raster("~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/pred_raster_hw.tif")
pred_raster_w <- raster("~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/pred_raster_w.tif")
zwe_adm3 <- st_read('/Users/sturrockh/Dropbox/Data to be shared/poverty data/poverty_adminzones/zwe_adm3_2002_v2_utm.shp')
poverty_df <- read.csv("/Users/sturrockh/Dropbox/Data to be shared/poverty data/poverty_adminzones/master_092518_simplified.csv")
poverty_df <- poverty_df[,c("wardpcode02_v2", "Foodpovertyprevalence")]
zwe_adm3 <- merge(zwe_adm3, poverty_df, by.x = "wardpcode0",
                    by.y = "wardpcode02_v2")
zwe_adm3 <- st_transform(zwe_adm3, crs(pred_raster_w))
zwe_adm3_sp <- as(zwe_adm3, "Spatial")
poverty_raster <- rasterize(zwe_adm3_sp, pred_raster_hw, field = "Foodpovertyprevalence")
names(poverty_raster) <- "poverty"
pop_dens <- raster('~/Documents/Work/Lnl/covid_modeling_ZWE/data/pop_dens_1km.tif')
#pop_dens <- aggregate(pop_dens, 30, sum, na.rm=T)
pop_dens <- resample(pop_dens, pred_raster_w)
pop_dens[is.na(pop_dens[])] <- 0
names(pop_dens) <- 'pop_dens'
dist_to_road <- raster("~/Documents/Work/Lnl/covid_modeling_ZWE/covariate_rasters/zwe_osm_dst_road_100m_2016.tif")
dist_to_road <- resample(dist_to_road, pop_dens)

# Combine handwashing/water
data_idx <- which(!is.na(pred_raster_hw[]))
hw_pca <- prcomp(cbind(pred_raster_hw[data_idx], pred_raster_w[data_idx]))
hw_pca_raster <- pred_raster_hw
hw_pca_raster[data_idx] <- hw_pca$x[,1]

covs <- stack(pred_raster_hw, 
              #pred_raster_w,
              #hw_pca_raster,
              dist_to_road,
              pop_dens, 
              poverty_raster)
names(covs) <- c("Handwashing_risk",
                 #"Water_risk",
                 #"hw_pca",
                 "Distance_to_road",
                 "Population_density",
                 "Poverty")



# Test
res <- prevalence_predictor_mgcv_st_grid(df_trim,
                                                     boundary = '~/Documents/Work/Lnl/covid_modeling_ZWE/data/ZWE_boundary.geojson',
                                                     covariates = covs,
                                                     ncol_pred_grid = 500,
                                                     m=1,
                                                     debug = TRUE)

res_improved_1 <- prevalence_predictor_mgcv_st_grid(df_trim,
                                                     boundary = '~/Documents/Work/Lnl/covid_modeling_ZWE/data/ZWE_boundary.geojson',
                                                     covariates = covs,
                                                     ncol_pred_grid = 500,
                                                    m=1,
                                                     debug = TRUE,
                                                      fix_prediction_covariates = list(Handwashing_risk = 0.24))

res_improved_2 <- prevalence_predictor_mgcv_st_grid(df_trim,
                                                     boundary = '~/Documents/Work/Lnl/covid_modeling_ZWE/data/ZWE_boundary.geojson',
                                                     covariates = covs,
                                                     ncol_pred_grid = 500,
                                                    m=1,
                                                     debug = TRUE,
                                                      fix_prediction_covariates = list(Handwashing_risk = 0.036))

res_improved_3 <- prevalence_predictor_mgcv_st_grid(df_trim,
                                                     boundary = '~/Documents/Work/Lnl/covid_modeling_ZWE/data/ZWE_boundary.geojson',
                                                     covariates = covs,
                                                     ncol_pred_grid = 500,
                                                    m=1,
                                                     debug = TRUE,
                                                      fix_prediction_covariates = list(Handwashing_risk = 0))



# Generate district level pop-weighted means
zwe_adm2 <- readRDS('/Users/sturrockh/Documents/Work/Lnl/covid_modeling_ZWE/gadm36_ZWE_2_sp.rds')
zwe_adm2 <- st_as_sf(zwe_adm2)
res_resamp <- resample(res$pred_prev_raster, pop_dens)
res_improved_1_resamp <- resample(res_improved_1$pred_prev_raster, pop_dens)
res_improved_2_resamp <- resample(res_improved_2$pred_prev_raster, pop_dens)
res_improved_3_resamp <- resample(res_improved_3$pred_prev_raster, pop_dens)
sum(res_resamp[] * pop_dens[], na.rm=T) / sum(pop_dens[],na.rm=T)
sum(res_improved_1_resamp[] * pop_dens[], na.rm=T) / sum(pop_dens[],na.rm=T)
sum(res_improved_2_resamp[] * pop_dens[], na.rm=T) / sum(pop_dens[],na.rm=T)
sum(res_improved_3_resamp[] * pop_dens[], na.rm=T) / sum(pop_dens[],na.rm=T)

writeRaster(res_resamp, overwrite = TRUE, "~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/resp_illness_prev.tif")
writeRaster(res_improved_1_resamp, overwrite = TRUE, "~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/resp_illness_improved_1_prev.tif")
writeRaster(res_improved_2_resamp, overwrite = TRUE, "~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/resp_illness_improved_2_prev.tif")
writeRaster(res_improved_3_resamp, overwrite = TRUE, "~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/resp_illness_improved_3_prev.tif")

# Create pop-weighted district means
zwe_adm2$total_pop <- extract(pop_dens, zwe_adm2, sum, na.rm=T)
weighted_sum_res <- extract(res_resamp*pop_dens, zwe_adm2, sum, na.rm=T)
weighted_sum_res_improved_1 <- extract(res_improved_1_resamp*pop_dens, zwe_adm2, sum, na.rm=T)
zwe_adm2$mean_resp_risk_pop_weighted <- weighted_sum_res / zwe_adm2$total_pop
zwe_adm2$mean_resp_risk_improved_1_pop_weighted <- weighted_sum_res_improved_1 / zwe_adm2$total_pop
weighted_sum_res_improved_2 <- extract(res_improved_2_resamp*pop_dens, zwe_adm2, sum, na.rm=T)
zwe_adm2$mean_resp_risk_improved_2_pop_weighted <- weighted_sum_res_improved_2 / zwe_adm2$total_pop
weighted_sum_res_improved_3 <- extract(res_improved_3_resamp*pop_dens, zwe_adm2, sum, na.rm=T)
zwe_adm2$mean_resp_risk_improved_3_pop_weighted <- weighted_sum_res_improved_3 / zwe_adm2$total_pop
write.csv(st_drop_geometry(zwe_adm2),
          "~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/district_resp_risk.csv", row.names = F)

# Create ward level
zwe_adm3$total_pop <- extract(pop_dens, zwe_adm3, sum, na.rm=T)
weighted_sum_res_ward <- extract(res_resamp*pop_dens, zwe_adm3, sum, na.rm=T)
weighted_sum_res_improved_1_ward <- extract(res_improved_1_resamp*pop_dens, zwe_adm3, sum, na.rm=T)
zwe_adm3$mean_resp_risk_pop_weighted <- weighted_sum_res_ward / zwe_adm3$total_pop
zwe_adm3$mean_resp_risk_improved_1_pop_weighted <- weighted_sum_res_improved_1_ward / zwe_adm3$total_pop
weighted_sum_res_improved_2_ward <- extract(res_improved_2_resamp*pop_dens, zwe_adm3, sum, na.rm=T)
zwe_adm3$mean_resp_risk_improved_2_pop_weighted <- weighted_sum_res_improved_2_ward / zwe_adm3$total_pop
weighted_sum_res_improved_3_ward <- extract(res_improved_3_resamp*pop_dens, zwe_adm3, sum, na.rm=T)
zwe_adm3$mean_resp_risk_improved_3_pop_weighted <- weighted_sum_res_improved_3_ward / zwe_adm3$total_pop
write.csv(st_drop_geometry(zwe_adm3[,c('wardpcode0', 'mean_resp_risk_pop_weighted', 
                                       'mean_resp_risk_improved_1_pop_weighted',
                                       'mean_resp_risk_improved_2_pop_weighted',
                                       'mean_resp_risk_improved_3_pop_weighted')]),
          "~/Documents/Work/Lnl/covid_modeling_ZWE/outputs/ward_resp_risk.csv", row.names = F)
save(list=ls(), file = "~/Documents/Work/Lnl/covid_modeling_ZWE/data/resp_illness_layers_data.RData")
```

To map the prevalence of respiratory illness across Zimbabwe, we used data from the latest DHS. Specifically, we extracted data on the presence of symptoms related to respiratory ilness in children (cough, fever, shortness of breath). 

```{r, echo=FALSE, warning=F, message=F}
library(sf)
library(mgcv)
library(raster)
library(lubridate)
library(sf)
library(disarmr)
library(gratia)
library(leaflet)
library(wesanderson)
library(knitr)
#opts_chunk$set(fig.width=10, fig.height=8)
load("~/Documents/Work/Lnl/covid_modeling_ZWE/data/resp_illness_layers_data.RData")
df_trim_sf <- st_as_sf(df_trim, coords = c('lng', 'lat'))
df_trim_sf$prevalence_respiratory_illness <- df_trim_sf$n_positive / df_trim_sf$n_trials
quick_map(df_trim_sf, 'prevalence_respiratory_illness')
```


These were modeled against a set of potential covariates including population density, distance to nearest road, poverty and handwashing risk as part of a spatial model. 

```{r, echo=FALSE}
plot(covs)
```

The figure below shows the relationship between respiratory illness and each risk factor. This shows that communities with higher handwashing risk, higher population density and those closer to roads had higher risk fo respiratory illness.

```{r, echo=FALSE, warning=FALSE}
# Generate diagnostic plots
draw(res$diagnostics$model)
```

Plots of observed versus fitted prevalence at the cluster level show a reasonable model fit, with a tendency to predict towards the mean.
```{r, echo=FALSE}
library(ggplot2)
ggplot(res$diagnostics$obs_fitted) + geom_point(aes(fitted, obs)) + xlim(0,1) + ylim(0,1)
```


This model was used to produce predicted prevalence of respiratory illness (symptoms) on a 1km grid. We also estimated the prevalence of respiratory illness under two scenarios of i) reducing handwashing risk to 0.24 (lowest observed district level value) everywhere, ii) reducing handwashing risk to 0.036 (lowest observed cluster level value) and iii) reducing handwashing risk to 0 everywhere. 
```{r, echo=FALSE}
colors <- wes_palette("Zissou1", 10, type = "continuous")[1:10]
col_pal <- colorNumeric(colors, c(0.02, 0.74), na.color = NA)
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% 
  addRasterImage(res$pred_prev_raster, col = col_pal, opacity = 0.8,
                 group = "Current") %>%
    addRasterImage(res_improved_1$pred_prev_raster, col = col_pal, opacity = 0.8,
                  group = "Improved handwashing scenario 1") %>%
  addRasterImage(res_improved_2$pred_prev_raster, col = col_pal, opacity = 0.8,
                 group = "Improved handwashing scenario 2") %>%
    addRasterImage(res_improved_3$pred_prev_raster, col = col_pal, opacity = 0.8,
                 group = "Improved handwashing scenario 3") %>%
  addLegend(pal = col_pal, values = c(0.02, 0.74), 
            title = "Prevalence of respiratory <br> illness symptoms") %>%
  addLayersControl(baseGroups = c("Current", 
                                  "Improved handwashing scenario 1", 
                                  "Improved handwashing scenario 2",
                                  "Improved handwashing scenario 3")) 
```

Overall, it is estimated that reducing handwashing risk throughout the country to the minimum observed at district level (0.24) in Zimbabwe would lead to a reduction in the prevalence of respiratory illness from 40.5% to 33.6%. Redicing handwashing risk to 0.036 would reduce the prevalence of respiratory illness to 15.6% and reducing handwashing risk to 0 (i.e. ensuring every household has access to water and handwashing facilities) would reduce the prevalence of respiratory illness to 13.8%.

To obtain district and ward level prevalence estimates under current and improved scenarios, we calculated the population weighted mean. 
```{r, echo=FALSE, warning=FALSE}
#poverty_sf_simp <- st_simplify(poverty_sf, dTolerance=0.01)
basemap <- leaflet() %>% addProviderTiles("CartoDB.Positron")
col_pal <- colorNumeric(wesanderson::wes_palette("Zissou1", 64, type='continuous')[1:64],
                        c(0, 0.61))

basemap %>% addPolygons(data = zwe_adm2, 
                        color = "black",
                        weight = 1,
                        fillOpacity = 0.8,
                        popup = zwe_adm2$NAME_2,
                        fillColor = col_pal(zwe_adm2$mean_resp_risk_pop_weighted),
                        group = "District") %>%
  
addPolygons(data = zwe_adm2, 
                        color = "black",
                        weight = 1,
                        fillOpacity = 0.8,
                        popup = zwe_adm2$NAME_2,
                        fillColor = col_pal(zwe_adm2$mean_resp_risk_improved_1_pop_weighted),
                        group = "District (improved WASH scenario 1)") %>%
  
addPolygons(data = zwe_adm2, 
                        color = "black",
                        weight = 1,
                        fillOpacity = 0.8,
                        popup = zwe_adm2$NAME_2,
                        fillColor = col_pal(zwe_adm2$mean_resp_risk_improved_2_pop_weighted),
                        group = "District (improved WASH scenario 2)") %>%
  
  addPolygons(data = zwe_adm2, 
                        color = "black",
                        weight = 1,
                        fillOpacity = 0.8,
                        popup = zwe_adm2$NAME_2,
                        fillColor = col_pal(zwe_adm2$mean_resp_risk_improved_3_pop_weighted),
                        group = "District (improved WASH scenario 3)") %>%
  
  addLegend(pal = col_pal,
            values = c(0, 0.61),
            title = "Prevalence of <br> respiratory illness") %>%
  
  addLayersControl(baseGroups = c("District", 
                                  "District (improved WASH scenario 1)",
                                  "District (improved WASH scenario 2)",
                                  "District (improved WASH scenario 3)"),
                   options = layersControlOptions(collapsed = F))
```

